%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage[sfdefault,extralight]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

\name{Sam Swanke}
\address{skswanke@gmail.com \textcolor{MYBLUE}{\textbullet} samswanke.com}
\address{New York, NY}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

Engineering leader with Amazon and startup CTO experience. At Amazon, delivered platforms enabling nine-figure insurance contracts and supporting hundreds of nonprofit partners processing tens of thousands of annual cases. As CTO, led a zero-downtime AWS migration while contributing significant code — dramatically improving API performance and operational stability. Deeply invested in growing engineers: coached multiple promotions at Amazon, developed a non-technical hire into an effective engineer, and retained the entire team through a demanding rebuild. Combines distributed systems depth with a leadership style that elevates people and ships results.

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------
% HelloPrenup

\begin{rSubsection}{HelloPrenup}{Dec 2024 -- Present}{Chief Technology Officer}{New York, NY}

Built and led the engineering team at an early-stage (20 person) legal technology company, owning hiring, architecture, and delivery of customer-facing distributed systems.

\begin{itemize}
  \item Built the engineering organization from zero, hiring and onboarding 4 engineers; \textbf{retained 100\%} of the team through a high-pressure 9-month platform rebuild.
  \item Owned the full hiring funnel, sourcing and screening from 300+ candidates across phone, technical, and onsite rounds hiring top talent within tight budget constraints.
  \item Coached a non-technical employee into an effective junior engineer on track to reach mid-level; created performance guidelines and calibrated each engineer against clear expectations.
  \item Reduced new-hire time-to-productivity to \textbf{2 weeks} through structured onboarding and comprehensive system documentation, even during a full platform rebuild.
  \item Led migration from a monolithic no-code platform to a stateless, horizontally scalable AWS architecture; executed \textbf{zero-downtime cutover} while maintaining uninterrupted customer service for 5-10k monthly active users.
  \item Delivered production launch handling \textbf{8M+ monthly requests} with 130ms average response times; contributed 30\% of code changes while establishing durable architectural patterns.
  \item Reduced customer support tickets by \textbf{44\%}, improved page load times by \textbf{61\%}, and reduced API response times by \textbf{91\%} through architectural and performance improvements.
\end{itemize}

\end{rSubsection}

%------------------------------------------------
% AMAZON

\begin{rSubsection}{Amazon}{May 2022 -- Dec 2024}{Software Development Manager}{New York, NY}

Led a team of 8 (5 direct-report SDEs, 1 Sr. SDE, 1 PM-T, 1 TPM) building large-scale, highly reliable internal platforms for Amazon Treasury's Global Risk Management \& Claims organization, partnering with product, finance and claims teams.

\begin{itemize}
  \item Took ownership of a mission-critical insurance request platform \textbf{4 weeks before launch} following external vendor (ProServe) handoff; drove cutover plan, reprioritized scope, and delivered a stable production launch.
  \item Led structured handover deep-dive: triaged 65 issues, delivered \textbf{47 launch-critical fixes}, including 33 bugs, 9 data-integrity gaps, and 5 configuration defects prior to go-live.
  \item Enabled procurement workflows supporting \textbf{nine-figure} insurance contracts by delivering a reliable, auditable system under aggressive deadlines.
  \item Designed and launched distributed case-management workflows supporting \textbf{over 750} nonprofit partners and \textbf{~30,000} annual cases, using AWS-native services and event-driven orchestration.
  \item Improved engineering quality and operational readiness: raised unit test coverage from \textbf{~5\% → 40\%}, introduced production readiness gates, and strengthened monitoring/alerting to reduce regressions.
  \item Reduced weekly on-call incidents by \textbf{~50\%} through improved test strategy, better operational processes, and targeted architectural simplification.
  \item Managed and mentored 5 engineers; coached \textbf{2} engineers through successful \textbf{L4→L5} promotions and expanded ownership across system areas.
  \item Navigated shifting org priorities (including deprioritization of a flagship product) while maintaining team morale, delivery predictability, and customer trust.
\end{itemize}

\end{rSubsection}
\begin{rSubsection}{Amazon}{Aug 2021 -- May 2022}{Software Development Engineer II}{New York, NY}

\begin{itemize}
  \item Led architecture and implementation of a greenfield distributed service using AWS-native infrastructure, designing scalable data models and workflows for complex business processes.
  \item Served as front-end technical lead and mentor, carved a pathway to promotion into engineering management.
\end{itemize}

\end{rSubsection}

%------------------------------------------------
% FEATHER

\begin{rSubsection}{Feather}{Dec 2019 -- Jul 2021}{Senior Software Engineer}{New York, NY}

\begin{itemize}
  \item Led development of internal tools streamlining operational workflows and reducing manual overhead. Improved site performance through frontend optimizations, which reduced load times by \textbf{30\%}.
\end{itemize}

\end{rSubsection}

%------------------------------------------------
% CALA

\begin{rSubsection}{CALA}{Aug 2018 -- Nov 2019}{Software Engineer}{New York, NY}

\begin{itemize}
  \item Engineer \#2 at a fashion technology startup; helped scale the engineering team and build core platform features supporting product design, production tracking, and fulfillment.
\end{itemize}

\end{rSubsection}

%------------------------------------------------
% DEALER

\begin{rSubsection}{Dealer.com}{May 2016 -- Aug 2018}{Software Engineer / Intern}{Burlington, VT}

\begin{itemize}
  \item Built data-processing libraries to canonicalize large-scale customer data and developed maintainable frontend applications in Java and Angular. Shared modern frontend best practices through internal technical talks.
\end{itemize}

\end{rSubsection}

%------------------------------------------------
% COSECHANDO FELICIDAD

\begin{rSubsection}{Cosechando Felicidad Inc}{Aug 2015 -- Present}{Front-End Engineer (Volunteer)}{Remote}

\begin{itemize}
  \item Sole developer for HarvestingHappiness.org, supporting a nonprofit serving vulnerable communities through long-term volunteer engagement.
\end{itemize}

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Vermont} \\
Bachelor of Science in Computer Science, 
Minor in Mathematics \hfill {May 2017}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{itemize}
  \item \textbf{Engineering Leadership:} Incident management, on-call operations, hiring and onboarding, performance management, delivery planning, architecture and design
  \item \textbf{Infrastructure:} AWS (compute, storage, messaging, observability), CI/CD, infrastructure as code
  \item \textbf{Languages:} TypeScript / JavaScript, Java, Python, C++
  \item \textbf{Systems \& Frameworks:} React, Node.js, API design, distributed systems
  \item \textbf{Data:} PostgreSQL, MySQL, DynamoDB
\end{itemize}

\end{rSection}

\end{document}
